\documentclass[12pt, signed]{UConnLH}
\usepackage{url}

\begin{document}
\to{Tyler Kleykamp}{Office of Policy and Managment, CT}

\opening{Dear Tyler,}

The Department of Statistics of the University of Connecticut (UCONN)
is proud to host the 33rd New England Statistics Symposium (NESS) on
May 15--17, 2019. As an annual event, NESS has been bringing together
statisticians from all over New England to a central location to share
research, discuss emerging issues in the field, and network with
colleagues since it was first started at UConn in 1987. After the
establishment of the New England Statistical Society in 2017, we are
proud to host the first remodeled NESS to bring NESS to a new
level. The symposium (\url{https://symposium.nestat.org/}) will be a
3-day event, featuring short courses, plenary talks, invited sessions,
career development panel discussion, student paper competition,
student poster competition, statathon, and Chernoff Lecture. In
addition to being a larger scale event, two new features are the
stat-a-thon and the Chernoff Lecture.


In order for the conference to be successful, we are actively seeking
corporate support. A wide variety of application areas will be covered
by the invited sessions, which may be of interests to your
statistical/analytic teams. Potential collaboration between your
corporation and our department on research development and on
recruitment/internship can benefit both sides.
Donations will be used to defray part of the expenses of the program
book printing, travel expenses of the keynote speakers, the opening
reception, the wireless network, and registration fees for students
who present at the symposium. Every financial
commitment made as an advertiser, exhibitor, or sponsor counts
toward NESS sponsorship status. As a Platinum (\$5000), Gold
(\$3000), or Silver (\$1000) sponsor, you will receive different levels
of recognition for your support.
We would appreciate it if you can kindly pass our
sponsorhip request to the right chanel in your coporation.


If you have further questions, please feel free to contact me

\closing

%\encl{}
%\cc{}

\end{document}
